Adolescent well-being in the digital age

### 2022-01-20 00-clean.qmd
Quarto book

```{r setup}
#| cache: false
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(lubridate)
library(gtsummary)
library(kableExtra)
library(tidyverse)

@@

```{r gallup-codebook}
#| echo: false
#| eval: false
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/The_Gallup_101521.sav",
  n_max = 1,
  col_select = c(
    WPID, WP1219,
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74
  )
) %>%
  generate_dictionary()
```

@@

```{r gallup-clean}
# First liberate the data from the slow SPSS file and save to disk
gwp_path <- "data-raw/Gallup/gwp-processed.rds"
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    "data-raw/Gallup/The_Gallup_101521.sav",
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )

@@

gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

@@

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    se = sd(val, na.rm = TRUE) / sqrt(n()),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```

@@

```{r gwp-harmonise-countries}
#| results: hold
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing and therefore the original name is retained."

@@

```{r}
# Create if doesn't exist
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (!file.exists(gwp_mock_path)) {
  distinct(gwp, outcome, country, year, sex, age) %>% 
    mutate(
      se = rnorm(
        nrow(.), 
        mean(gwp$se, na.rm = TRUE), 
        sd(gwp$se, na.rm = TRUE)
      ),
      val = rnorm(
        nrow(.), 
        mean(gwp$val, na.rm = TRUE), 
        sd(gwp$val, na.rm = TRUE)
      )
    ) %>% 
    write_rds(gwp_mock_path, compress = "xz")
}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

@@

```{r gbd-harmonise-countries}
#| results: hold
#| label: tbl-gbd-countries
#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

@@

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "Countries whose original ITU name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

@@

>>>>

```{r setup}
#| cache: false
#| results: hide
#| message: false
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(lubridate)
library(gtsummary)
library(kableExtra)
library(tidyverse)

@@

```{r gallup-codebook}
#| echo: false
#| eval: false
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/The_Gallup_101521.sav",
  n_max = 1,
  col_select = c(
    WPID, WP1219,
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74,
    WP16056
  )
) %>%
  generate_dictionary()
```

@@

```{r gallup-clean}
# First liberate the data from the slow SPSS file and save to disk
gwp_path <- "data-raw/Gallup/gwp-processed.rds"
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    "data-raw/Gallup/The_Gallup_101521.sav",
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74,
      WP16056
    )
  )

@@

gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .),
    # Internet (fix NAs and reverse 1:yes 2:no coding to 1:no 2:yes)
    gwpi = 2 - if_else(between(wp16056, 1, 2), wp16056, NaN)
  )

@@

```{r gallup-summarise}
gwp <- gwp %>%
  # Aggregate internet
  group_by(country, year, sex, age) %>% 
  mutate(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome, gwpi) %>%
  summarise(
    se = sd(val, na.rm = TRUE) / sqrt(n()),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```

@@

```{r gwp-harmonise-countries}
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing and therefore the original name is retained."

@@

```{r}
# Create if doesn't exist
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (!file.exists(gwp_mock_path)) {
  set.seed(101010)
  distinct(gwp, outcome, country, year, sex, age, gwpi) %>% 
    mutate(
      se = rnorm(
        nrow(.), 
        mean(gwp$se, na.rm = TRUE), 
        sd(gwp$se, na.rm = TRUE)
      ),
      val = rnorm(
        nrow(.), 
        mean(gwp$val, na.rm = TRUE), 
        sd(gwp$val, na.rm = TRUE)
      )
    ) %>% 
    write_rds(gwp_mock_path, compress = "xz")
}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

@@

```{r gbd-harmonise-countries}
#| label: tbl-gbd-countries
#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"

@@

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "Countries whose original ITU name is different to the harmonised one, or whose harmonised name is missing"

@@

## GWP summary table

```{r gwp-summary-table}
#| column: page-right
#| tbl-cap: "Mean internet user percentages across regions and time from the GWP data."
#| label: tbl-gwpsummary

gwp %>%
  select(region, country, year, gwpi) %>%
  mutate(internet = internet * 100) %>%
  mutate(region = str_replace(region, "_", " ")) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra(caption = "ITU summary") %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```

### 2022-01-20 00-models.qmd
Quarto book

# Centering predictors within and between countries
itu <- itu %>%
  group_by(country) %>%
  mutate(
    i1_cb = mean(i1, na.rm = TRUE), # Country average
    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
    f1_cb = mean(f1, na.rm = TRUE),
    f1_cw = f1 - f1_cb,
    m1_cb = mean(m1, na.rm = TRUE),
    m1_cw = m1 - m1_cb,
  ) %>%
  # Grand-mean center the country averages
  mutate(
    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
  )

@@

@@

@@

fits %>%
  mutate(
    fit2_m = map2(
      data, outcome,
      ~brm(
        formula = bf_2_m,
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-2-mobile")
      )
    )
  )
```

>>>>

# Centering predictors within and between countries
itu <- itu %>%
  group_by(country) %>%
  mutate(
    i1_cb = mean(i1, na.rm = TRUE), # Country average
    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
    f1_cb = mean(f1, na.rm = TRUE),
    f1_cw = f1 - f1_cb,
    m1_cb = mean(m1, na.rm = TRUE),
    m1_cw = m1 - m1_cb,
  ) %>%
  # Grand-mean center the country averages
  ungroup() %>% 
  mutate(
    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
  )

@@

We then create the lagged and centered GWP internet predictor. Note that this is at the level of demographics, not just a country average like in ITU.

```{r}
# Take only relevant variables to make this easier
gwpi <- dat %>% 
  filter(outcome == "Life_satisfaction") %>% 
  filter(year >= .5) %>% 
  select(region, country, year, sex, age, year, gwpi)

# Create lagged GWP internet
gwpi <- gwpi %>% 
  arrange(region, country, sex, age, year) %>% 
  group_by(region, country, sex, age) %>% 
  mutate(g1 = lag(gwpi, 1))

# Center GWP internet
gwpi <- gwpi %>%
  group_by(country) %>%
  mutate(
    g1_cb = mean(g1, na.rm = TRUE), # Country average
    g1_cw = g1 - g1_cb, # Year-specific deviation from country average
  ) %>%
  # Grand-mean center the country averages
  ungroup() %>% 
  mutate(
    g1_cb = g1_cb - mean(g1_cb, na.rm = TRUE)
  )

# Join to data (all outcomes)
dat <- left_join(dat, select(gwpi, -gwpi))
```

@@

bf_2_g <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + g1_cw * sex + g1_cw * age + g1_cb +
    (year * sex + year * age + g1_cw * sex + g1_cw * age | country) +
    (year * sex + year * age + g1_cw * sex + g1_cw * age | region),
  family = gaussian(),
  unused = ~outcome
)

@@

fits %>%
  mutate(
    fit2_m = map2(
      data, outcome,
      ~brm(
        formula = bf_2_m,
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-2-mobile")
      )
    )
  )

fits %>%
  mutate(
    fit2_g = map2(
      data, outcome,
      ~brm(
        formula = bf_2_g,
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-2-gwpinternet")
      )
    )
  )
```

```{r}
fits$data[[1]] %>% select(country, year, g1_cb) %>% drop_na(g1_cb)
```

### 2022-01-20 01-timecourses.qmd
Quarto book

```{r forest-trends}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of linear trends in outcomes"
#| label: fig-forest-trends
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

>>>>

```{r forest-trends}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of linear trends in outcomes. Shaded areas indicate approximate posterior densities of average and region-specific trends. Blue points are country-specific posterior means. Black points and lines are 95%CIs; open points indicate estimates where zero is within the 95% most credible values."
#| label: fig-forest-trends
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

### 2022-01-20 04-fixed-mobile.qmd
Quarto book

>>>>

Correspondence between different internet metrics. Note that

- ITU internet metrics are for everyone (all ages, genders, etc)
- GWP metrics are per demographic, aggregated to the country-year mean here (for 15 to 24 year olds!)

This helps to explain why, across the board, the ITU internet metric (`internet`, below) is lower than the GWP internet metric (`gwpi`) as younger people tend to have access to the internet more often (see e.g. [this ITU spreadsheet](https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_Oct_2021.xlsx) showing that the percentage of individuals using the internet is ~15% greater for youth (15-24) than the rest of the population.)

```{r}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "GWP and ITU internet metrics for all countries."
#| label: fig-internet-metrics
gwp %>% 
  group_by(region, country, year) %>% 
  summarise(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
  left_join(select(itu, country, year, internet)) %>% 
  filter(year >= 2015) %>% 
  pivot_longer(gwpi:internet) %>% 
  ggplot(aes(year, value, color = name)) +
  scale_color_brewer("Metric", palette = "Set1") +
  geom_line() +
  facet_wrap("country")
```

### 2022-01-20 index.qmd
Quarto book

Welcome! This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The data and source code repository, along with the datasets, are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

>>>>

Welcome! This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
